\markdownRendererHeadingOne{Week1: What is Machine Learning?}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Introduction}\markdownRendererInterblockSeparator
{}[Machine Learning] Field of study that gives computers thr ability to learn without being explicitly programmed. (older, informal)\markdownRendererInterblockSeparator
{}Improve performance from task experience. (more modern)\markdownRendererInterblockSeparator
{}\markdownRendererUlBegin
\markdownRendererUlItem A \markdownRendererStrongEmphasis{task}\markdownRendererUlItemEnd 
\markdownRendererUlItem Some \markdownRendererStrongEmphasis{experience}\markdownRendererUlItemEnd 
\markdownRendererUlItem Some way to \markdownRendererStrongEmphasis{measure}\markdownRendererUlItemEnd 
\markdownRendererUlEnd \markdownRendererInterblockSeparator
{}Two board type of ML algorithms:\markdownRendererInterblockSeparator
{}\markdownRendererUlBegin
\markdownRendererUlItem Supervised Learning\markdownRendererUlItemEnd 
\markdownRendererUlItem Unsupervised Learning\markdownRendererUlItemEnd 
\markdownRendererUlEnd \markdownRendererInterblockSeparator
{}Others:\markdownRendererInterblockSeparator
{}\markdownRendererUlBegin
\markdownRendererUlItem Reinforcement Learning\markdownRendererUlItemEnd 
\markdownRendererUlItem Recommender Systems\markdownRendererUlItemEnd 
\markdownRendererUlEnd \markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Supervised Learning}\markdownRendererInterblockSeparator
{}Supervised learning has some known relationship between input and output.\markdownRendererInterblockSeparator
{}Supervised learning problems are categorized into \markdownRendererStrongEmphasis{regression} and \markdownRendererStrongEmphasis{classification} problems.\markdownRendererInterblockSeparator
{}Fitting a straight line or quadratic or 2nd-order curve to a function is a regression. The main idea is to give a continuous solution based on data we have.\markdownRendererInterblockSeparator
{}Estimate weekly income of a company.\markdownRendererInterblockSeparator
{}Estimating some possbility to be certain type or classification is also a supervised learning.\markdownRendererInterblockSeparator
{}Classify tumor type based on its size.\markdownRendererInterblockSeparator
{}When the scale of classes turns to infinity, we need \markdownRendererStrongEmphasis{Support Vector Machine}.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Unsupervised Learning}\markdownRendererInterblockSeparator
{}Unsupervised learning has no specific relationship between input and output. Data has no lables, but the data could be devided into severval clusters.\markdownRendererInterblockSeparator
{}Unsupervised learning allows us to approach problems with little or no idea what our results should look like. We can derive structure from data where we don’t necessarily know the effect of the variables.\markdownRendererInterblockSeparator
{}Two recordings of audio are mixed, and computer should get them departed.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Linear Regression with One Variable}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Model and Cost Function}\markdownRendererInterblockSeparator
{}For a training set, Notation:\markdownRendererInterblockSeparator
{}\markdownRendererUlBegin
\markdownRendererUlItem $m$: number of training example\markdownRendererUlItemEnd 
\markdownRendererUlItem $x$: input variable / features\markdownRendererUlItemEnd 
\markdownRendererUlItem $y$: output variable / target variable\markdownRendererUlItemEnd 
\markdownRendererUlEnd \markdownRendererInterblockSeparator
{}Learning algorithm applis to training set to find a \markdownRendererStrongEmphasis{hypothesis} that could gives back a estimated answer.\markdownRendererInterblockSeparator
{}The goal of supervised learing is to learn a function (hypothesis) from the training set.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingThree{Cost Function}\markdownRendererInterblockSeparator
{}In a univariate problems, we have:\markdownRendererInterblockSeparator
{}$$h\markdownRendererEmphasis{\theta(x) = \theta}0 + \theta_1 x$$\markdownRendererInterblockSeparator
{}And the $\theta_i$ is so called \markdownRendererStrongEmphasis{Parameters}.\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Parameter Learning}\markdownRendererInterblockSeparator
{}\markdownRendererHeadingTwo{Linear Algebra Review}\relax